### 2018-05-24 write-up/abstract.tex
Finish Evaluation

As evidence for this argument, I show non-trivial, yet readable, linear algebra
programs, that are safe (with respect to aliasing, read/write permissions,
memory re-use and deallocation) and explicit (with respect to memory
allocation) which (1) are more memory-efficient than equivalent programs
written using purely high-level linear algebra libraries and (2) perform just
as predictably as equivalent programs written using low-level linear-algebra
libraries. I also argue \emph{the experience} of writing such programs with
linear types is ``better'' in key-respects. In addition to all of this, I show
that it is possible to provide such features \emph{as a library} on top of
existing programming languages and linear algebra libraries.

>>>>

As evidence for this argument, I show non-trivial, yet readable, linear algebra
programs, that are safe (with respect to aliasing, read/write permissions,
memory re-use and deallocation) and explicit (with respect to memory
allocation) which (1) are more memory-efficient than equivalent programs
written using high-level linear algebra libraries and (2) perform just
as predictably as equivalent programs written using low-level linear-algebra
libraries. I also argue \emph{the experience} of writing such programs with
linear types is qualitatively better in key-respects. In addition to all of
this, I show that it is possible to provide such features \emph{as a library}
on top of existing programming languages and linear algebra libraries.

### 2018-05-24 write-up/evaluation.tex
Finish Evaluation

\prechapter{%
    I will evaluate the central premise of this thesis: linear types are a
    practical and usable tool to help working programmers write readable, safe
    (with respect to aliasing, read/write permissions, memory re-use and
    deallocation) and explicit (with respect to memory allocation) code that
    (1) is more memory-efficient than code written using purely high-level
    linear algebra libraries and (2) performs just as predictably as code
    written using low-level linear-algebra libraries. I will also elaborate on
    the qualitative benefits of using linearly types to write linear-algebra
    programs.
}%

@@

I analysed four implmentations of a Kalman filter, increasing
the abstraction level at each step:

@@

    \item an Owl/OCaml implementation using a Cholesky decomposition
        (Figure~\ref{fig:chol_owl_kalman}) but not taking advantage of matrices
        known to be symmetric ahead of time, and producing a new temporary
        matrix for every operation (including inverse and tranpose)

    \item an idiomatic Owl/OCaml implmentation
        (Figure~\ref{fig:chol_owl_kalman}) with an explicit inverse (LU
        decomposition), not taking advantage of matrices known to be symmetric
        ahead of time, and producing a new temporary matrix for every operation
        (including inverse and tranpose).

@@

    \begin{minted}[linenos, fontsize=\small]{c}
static void kalman(
    const int n,               const int k,                const double *sigma, /* n,n */
    const double *h, /* k,n */ const double *mu, /* n,1 */ double *r,           /* k,k */
    double *data,    /* k,1 */ double **ret_mu,  /* k,1 */ double **ret_sigma   /* n,n */
) {
        double* k_by_n = (double *) malloc(k * n * sizeof(double));
/*20*/  cblas_dsymm(CblasRowMajor, CblasRight, CblasUpper, k, n, 1., sigma, n, h, n, 0., k_by_n, n);
/*21*/  cblas_dgemm(CblasRowMajor, CblasNoTrans, CblasTrans, k, k, n, 1., k_by_n, n, h, n, 1., r, k);
/*22*/  cblas_dgemm(CblasRowMajor, CblasNoTrans, CblasNoTrans, k, 1, n, 1., h, n, mu, 1, -1., data, 1);
/*23*/  cblas_dcopy(k * n, h, 1, k_by_n, 1);
        double* k_by_k = (double *) malloc(k * k * sizeof(double));
/*24*/  cblas_dcopy(k * k, r, 1, k_by_k, 1);
/*25*/  LAPACKE_dposv(LAPACK_ROW_MAJOR, 'U', k, n, k_by_k, k, k_by_n, n);
/*27*/  LAPACKE_dpotrs(LAPACK_ROW_MAJOR, 'U', k, 1, k_by_k, k, data, 1);
        free(k_by_k);
        double* n_by_n = (double *) malloc(n * n * sizeof(double));
/*28*/  cblas_dgemm(CblasRowMajor, CblasTrans, CblasNoTrans, n, n, k, 1., h, n, k_by_n, n, 0., n_by_n, n);
        free(k_by_n);
        double* n_by_1 = (double *) malloc(n * sizeof(double));
/*29*/  cblas_dgemm(CblasRowMajor, CblasTrans, CblasNoTrans, n, 1, k, 1., h, n, data, 1, 0., n_by_1, 1);
        double* new_mu = (double *) malloc(n * sizeof(double));
/*30*/  cblas_dcopy(n, mu, 1, new_mu, 1);
/*31*/  cblas_dsymm(CblasRowMajor, CblasLeft, CblasUpper, n, 1, 1., sigma, n, n_by_1, 1, 1., new_mu, 1);
        free(n_by_1);
        double* n_by_n2 = (double *) malloc(n * n * sizeof(double));
/*32*/  cblas_dsymm(CblasRowMajor, CblasRight, CblasUpper, n, n, 1., sigma, n, n_by_n, n, 0., n_by_n2, n);
/*33*/  cblas_dcopy(n*n, sigma, 1, n_by_n, 1);
/*34*/  cblas_dsymm(CblasRowMajor, CblasLeft, CblasUpper, n, n, -1., sigma, n, n_by_n2, n, 1., n_by_n, n);
        free(n_by_n2);
        *ret_sigma = n_by_n;
        *ret_mu = new_mu;
}
    \end{minted}
    \caption{CBLAS/LAPACKE implementation of a Kalman filter. I used C instead
        of Fortran because it is what Owl uses under the hood and OCaml FFI
        support for C is better and easier to use than that for Fortran. A distinct
        `measure\_kalman' function that sandwiches a call to this funtion with
        \texttt{getrusage} is omitted for brevity.}\label{fig:cblas_kalman}

@@

I evaluated the implmentations on two metrics: memory usage (via number and
size of temporaries allocated) and execution time. For the former, I compiled
Owl with print-statements on the relevant primitives to see exactly the number
of temporaries allocated for a single call of each function. While I did also
attempt to use gperftools and OCaml's profiling support with gprof for a more
holistic view of memory usage in the presence of OCaml's garbage-collector, I
ran into technical difficulties irrelevant to this thesis.

I measured execution time, in micro-seconds, against an exponentially (powers
of 5) increasing scaling factor for matrix size parameters $n=5$ and $k=3$.
For small scaling factors (1, 5, 25), I used the Core\_bench micro-benchmarking
library, for larger factors (125 and greater), I used the \texttt{getrusage}
system call (called \ltfla{Unix.times} in OCaml).  Core\_bench performs a
linear-regression (here, time against batch-size) so includes 95\%
confidence-interval with $R^2$. Larger scales have errors reported to $\pm
\sigma$ (one standard-deviation)

@@

Raw output of implementation traces and the benchmarking program (including
sample sizes) for each of the implementations are in
Appendix~\ref{chap:eval_data}.

@@

\begin{figure}[tp]
    \centering
    \input{timings.tex}
    \caption{Comparison of execution times. Small matrices and timings $n \le
        5^3$ were micro-benchmarked with the Core\_bench library. Larger ones used
    Unix's \texttt{getrusage} functionality.}\label{fig:timings}
\end{figure}

For $n=5$, and a per implementation sample size of around 450, the CBLAS
implementation is the fastest ($24\mu s$), followed by LT4LA ($41 \mu s$), then
Cholesky and Owl (around $52 \mu s$).  However, for $n=25$, and around 350
measurements per implementation, the idiomatic Owl implementation is the fastest
($95 \mu s$), \emph{then} CBLAS ($104 \mu s$), with LT4LA and Chol last (around
$130 \mu s$). The 95\% confidence-intervals around these measurements have been
between 0 and 2.

For $n=125$, and a per implementation sample size of around 110, the trends change:
CBLAS implmentation is now the \emph{slowest} ($1803 \mu s\, [1746,\, 1867]$).
This is followed by LT4LA ($1678 \mu s\, [1646,\, 1714]$) and Owl ($1488 \mu
s\, [1464,\, 1515]$). Chol had a low $R^2$ value ($0.74$) and so its execution
time is inconclusive here.

For $n=625$ and a sample size of 1000, Chol was now the fastest ($125.5 \pm
25\,ms$), then Owl ($146 \pm 32 \,ms$), followed by LT4LA ($180.5 \pm 38 \,ms$)
and CBLAS ($188 \pm 36 \, ms$). Despite the large sample size, the
standard-deviation is still quite high; however, calculating the pair-wise
$p$-values (Welch's t-test) suggests that the difference in the means is meaningful.

For $n=3125$, Chol takes approximately half the execution time ($11.4 \pm 2.7
\,s$) of the rest (differences between LT4LA, Owl and CBLAS were not
statistically significant, $p>.05$, using Welch's t-test) around $22s$.

\section{TO DO: Analysis}

Having access to primitives which allow a programmer to re-use memory means
that memory usage for temporaries in LT4LA is on par with that of C. One caveat
is that the `free\_mat' primitive is a no-op in LT4LA, which still relies on
OCaml's garbage-collector. The difference between these two implementations
and the idiomatic Owl implementation is $k(3n+2k+2)$ words, and

\section{TO DO: Limitations}

\section{TO DO: Qualitative Benefits}

>>>>

\prechapter{%
    I will evaluate the central premise of this thesis: linear types are a
    practical and usable tool to help working programmers write readable, safe
    (with respect to aliasing, read/write permissions, memory re-use and
    deallocation) and explicit (with respect to memory allocation) code that
    (1) is more memory-efficient than code written using high-level
    linear algebra libraries and (2) performs just as predictably as code
    written using low-level linear-algebra libraries. I will also elaborate on
    the qualitative benefits of using linear types to write linear-algebra
    programs.
}%

@@

I analysed four implementations of a Kalman filter, increasing
the abstraction level at each step:

@@

    \item an Owl/OCaml implementation using a Cholesky decomposition
        (Figure~\ref{fig:chol_owl_kalman}) but not taking advantage of matrices
        known to be symmetric ahead of time, and producing a new temporary
        matrix for every operation (including inverse and transpose)

    \item an idiomatic Owl/OCaml implementation
        (Figure~\ref{fig:chol_owl_kalman}) with an explicit inverse (LU
        decomposition), not taking advantage of matrices known to be symmetric
        ahead of time, and producing a new temporary matrix for every operation
        (including inverse and transpose).

@@

    \begin{minted}[linenos, fontsize=\small]{c}
static void kalman(
    const int n,               const int k,                const double *sigma, /* n,n */
    const double *h, /* k,n */ const double *mu, /* n,1 */ double *r,           /* k,k */
    double *data,    /* k,1 */ double **ret_mu,  /* k,1 */ double **ret_sigma   /* n,n */
) {
        double* k_by_n = (double *) malloc(k * n * sizeof(double));
/*20*/  cblas_dsymm(CblasRowMajor, CblasRight, CblasUpper, k, n, 1., sigma, n, h, n, 0., k_by_n, n);
/*21*/  cblas_dgemm(CblasRowMajor, CblasNoTrans, CblasTrans, k, k, n, 1., k_by_n, n, h, n, 1., r, k);
/*22*/  cblas_dgemm(CblasRowMajor, CblasNoTrans, CblasNoTrans, k, 1, n, 1., h, n, mu, 1, -1., data, 1);
/*23*/  cblas_dcopy(k * n, h, 1, k_by_n, 1);
        double* k_by_k = (double *) malloc(k * k * sizeof(double));
/*24*/  cblas_dcopy(k * k, r, 1, k_by_k, 1);
/*25*/  LAPACKE_dposv(LAPACK_ROW_MAJOR, 'U', k, n, k_by_k, k, k_by_n, n);
/*27*/  LAPACKE_dpotrs(LAPACK_ROW_MAJOR, 'U', k, 1, k_by_k, k, data, 1);
        free(k_by_k);
        double* n_by_n = (double *) malloc(n * n * sizeof(double));
/*28*/  cblas_dgemm(CblasRowMajor, CblasTrans, CblasNoTrans, n, n, k, 1., h, n, k_by_n, n, 0., n_by_n, n);
        free(k_by_n);
        double* n_by_1 = (double *) malloc(n * sizeof(double));
/*29*/  cblas_dgemm(CblasRowMajor, CblasTrans, CblasNoTrans, n, 1, k, 1., h, n, data, 1, 0., n_by_1, 1);
        double* new_mu = (double *) malloc(n * sizeof(double));
/*30*/  cblas_dcopy(n, mu, 1, new_mu, 1);
/*31*/  cblas_dsymm(CblasRowMajor, CblasLeft, CblasUpper, n, 1, 1., sigma, n, n_by_1, 1, 1., new_mu, 1);
        free(n_by_1);
        double* n_by_n2 = (double *) malloc(n * n * sizeof(double));
/*32*/  cblas_dsymm(CblasRowMajor, CblasRight, CblasUpper, n, n, 1., sigma, n, n_by_n, n, 0., n_by_n2, n);
/*33*/  cblas_dcopy(n*n, sigma, 1, n_by_n, 1);
/*34*/  cblas_dsymm(CblasRowMajor, CblasLeft, CblasUpper, n, n, -1., sigma, n, n_by_n2, n, 1., n_by_n, n);
        free(n_by_n2);
        *ret_sigma = n_by_n;
        *ret_mu = new_mu;
}
    \end{minted}
    \caption{CBLAS/LAPACKE implementation of a Kalman filter. I used C instead
        of Fortran because it is what Owl uses under the hood and OCaml FFI
        support for C is better and easier to use than that for Fortran. A distinct
        `measure\_kalman' function that sandwiches a call to this function with
        \texttt{getrusage} is omitted for brevity.}\label{fig:cblas_kalman}

@@

I evaluated the implementations on two metrics: memory usage (via number and
size of temporaries allocated) and execution time. For the former, I compiled
Owl with print-statements on the relevant primitives to see exactly the number
of temporaries allocated for a single call of each function. While I did also
attempt to use gperftools and OCaml's profiling support with gprof for a more
holistic view of memory usage in the presence of OCaml's garbage-collector, I
ran into technical difficulties irrelevant to this thesis.

I measured execution time, in micro-seconds, against an exponentially (powers
of 5) increasing scaling factor for matrix size parameters $n=5$ and $k=3$.
For small scaling factors (1, 5, 25), I used the Core\_bench micro-benchmarking
library, for larger factors (125 and greater), I used the \texttt{getrusage}
system call (called \ltfla{Unix.times} in OCaml), sandwiched between calls to
\ltfla{Gc.full_major} to ensure no garbage collection took place during the
measurements.  Core\_bench performs a linear-regression (here, time against
batch-size) so includes 95\% confidence-interval with $R^2$. Larger scales have
errors reported to $\pm \sigma$ (one standard-deviation)

@@

All implementations produce the same answers (within at most $2^{-52}$). Raw
output of implementation traces and the benchmarking program (including sample
sizes) for each of the implementations are in Appendix~\ref{chap:eval_data}.

@@

\begin{figure}[tp]
    \centering
    \input{timings.tex}
    \caption{Comparison of execution times. Small matrices and timings $n \le
        5^3$ were micro-benchmarked with the Core\_bench library. Larger ones used
        Unix's \texttt{getrusage} functionality, sandwiched between calls to
        \ltfla{Gc.full_major} for the OCaml implementations.}\label{fig:timings}

For $n=5$, and a per implementation sample size of around 450, the CBLAS
implementation is the fastest ($24\mu s$), followed by LT4LA ($41 \mu s$), then
Cholesky and Owl (around $52 \mu s$).  However, for $n=25$, and around 350
measurements per implementation, the idiomatic Owl implementation is the fastest
($95 \mu s$), \emph{then} CBLAS ($104 \mu s$), with LT4LA and Chol last (around
$130 \mu s$). The 95\% confidence-intervals around these measurements are
between 0 and 2.

For $n=125$, and a per implementation sample size of around 110, the trends change:
CBLAS implementation is now the \emph{slowest} ($1803 \mu s\, [1746,\, 1867]$).
This is followed by LT4LA ($1678 \mu s\, [1646,\, 1714]$) and Owl ($1488 \mu
s\, [1464,\, 1515]$). Chol had a low $R^2$ value ($0.74$) and so its execution
time is inconclusive here.

For $n=625$ and a sample size of 1000, Chol was now the fastest ($125.5 \pm
25\,ms$), then Owl ($146 \pm 32 \,ms$), followed by LT4LA ($180.5 \pm 38 \,ms$)
and CBLAS ($188 \pm 36 \, ms$). Despite the large sample size, the
standard-deviation is still quite high; however, \emph{because} of the large
sample size, the pair-wise $p$-values (Welch's t-test) are very small ($p <
.05$), suggesting that the difference in the means is statistically
significant.

For $n=3125$ and a sample size of 15, Chol and Owl had similar mean execution
times ($11.2 \pm 0.85 \,s$ and $12.1 \pm 0.47 \,s$ respectively) while LT4LA
and CBLAS had similar, but \emph{slower} mean execution times ($16.1 \pm 0.19
\,s$ and $15.7 \pm 0.53 \,s$ respectively). Pair-wise $p$-values (Welch's
t-test) are all less than $.05$, so the differences in means are statistically
significant.

\section{Analysis}

Having access to primitives which allow a programmer to re-use memory means
that memory usage for temporaries in LT4LA is on par with that of CBLAS. One
caveat is that the \ltfla{freeM} primitive is a no-op in LT4LA, so deallocation
still relies on OCaml's garbage-collector. The difference between these two
implementations and the idiomatic Owl implementation is $k(3n+2k+2)$ words.

For small matrix sizes, LT4LA and CBLAS execution times differ. I suspect this
is due to large sample sizes causing more allocations and thus more
garbage-collector unpredictability (which the linear-regression \emph{did not}
take into account; multi-variate regressions are not fully supported
Core\_bench yet).

As matrix size increases, execution times of LT4LA become very similar to those
of CBLAS. However, that does not necessarily mean faster.  Especially for
$n=625$ and $n=3125$ (sizes for which \ltfla{Gc.full_major} was called before
each measurement), mean execution times start to split clearly into two groups:
Chol and Owl as one group (similar, faster times) and LT4LA and CBLAS as
another (similar, slower times).

Overall, as far as memory usage is concerned, it is possible to write linear
algebra programs with the safety (with respect to aliasing and read/write
permissions) of using high-level libraries whilst gaining the explicit control
over memory allocation and re-use associated with low-level libraries.
As far as execution times are concerned, even though the idiomatic OCaml
implementations seem to be faster for this particular
benchmark,\footnote{Attempting to understand \emph{why} the
    Chol/Owl implementations tended to be faster for anything except the
    smallest of matrices, despite allocating almost twice the number of
    temporaries was difficult. Running the different implementations through
    the Cachegrind cache simulator (part of Valgrind) showed that LT4LA/CBLAS
    had a roughly 1\% higher cache miss rate than Chol/Owl (rising from around
    11\% to around 12\%). This seemed insufficient to account for the
    differences, so I investigated further. I added an extra, modified
    implementation of LT4LA, which transposed the `h' parameter into a new
    matrix rather than using the transpose flag to `gemm', to see if
    row-vs-column access patterns could account for the differences (they did
    not). Had I been able to use gprof or gperftools, I would have profiled the
    remaining key difference: the `symm' routine (which performs \emph{half} as
    many multiplications as `gemm' because it knows one of its
    arguments is symmetric).}
we can conclude that LT4LA performs similarly to using lower-level libraries
when garbage-collection is controlled for and especially as matrix sizes increase.

\section{Limitations}

I chose the example of a Kalman filter because it is used in the real world,
consists purely of a sequence of matrix expressions and produces many
unnecessary temporary matrices when implemented idiomatically in a high-level
linear-algebra library. It is good for isolating the key differences between
not having and having linear types to help a programmer safely manage memory
and aliasing, whilst excluding other aspects also important to real world
linear-algebra programs such as control flow or blocking.

\section{Qualitative Benefits}

Prior to this project, I had no experience with linear-algebra libraries or the
problem of matrix expression compilation. As such, I based my initial LT4LA
implementation of a Kalman filter using BLAS and LAPACK, on a popular GitHub
gist of a Fortran implementation, one that was automatically generated from
SymPy's matrix expression compiler~\cite{rocklin_thesis}.

Once I translated the implementation, I attempted to compile it and found that
(to my surprise) it did not type-check. This was because the original
implementation contained incorrect aliasing, did not adhere to Fortran's
read/write permissions (with respect to \texttt{intent} annotations
\texttt{in}, \texttt{out} and \texttt{inout}) and unused and unnecessary
temporaries, all of which were now highlighted by LT4LA's type system.

The original implementation used 6 temporaries, one of which was immediately
spotted as not being used due to linearity. It also contained two variables
which were marked as \texttt{intent(in)} but would have been written over by
calls to `gemm', spotted by the fractional-capabilities feature. Furthermore,
it used a matrix \emph{twice} in a call to `symm', once with a read permission
but once with a \emph{write} permission.  Fortran assumes that any parameter
being written to is not aliased and so this call was not only incorrect, but
illegal according to the standard, both aspects of which were captured by
linearity and fractional-capabilities. Lastly, it contained another unnecessary
temporary, however one that was not obvious without linear types. To spot it, I
first performed live-range splitting (checked by linearity) by hoisting calls
to \ltfla{freeM} and then annotated the freed matrices with their dimensions.
After doing so and spotting two disjoint live-ranges of the same size, I
replaced a call to \ltfla{freeM} followed by allocating call to \ltfla{copy}
with one, in-place call to \ltfla{copyM_to}.

\section{Summary}

Writing a linear-algebra program using LT4LA gives a programmer both
\emph{explicit control} (over read/write permissions, aliasing and memory
allocation, re-use and deallocation) and \emph{signals intent} to the compiler
and reader clearly without sacrificing either of readability or
value-semantics. The resulting programs perform similarly to equivalent
programs written directly using lower-level linear-algebra libraries. In turn,
the programs written can be \emph{checked automatically} against their intent,
especially when \emph{refactoring} or \emph{rewriting} code. Although any
expert \emph{could} have followed the same line of reasoning laid out above,
and arrived at the same program, LT4LA's type system enables a non-expert
(yours truly) to do the same and increase confidence in the result\footnote{As
always, this does not preclude testing code by actually executing it, but
definitely \emph{complements} it.} by checking said line of reasoning.

### 2018-05-24 write-up/implementation.tex
Finish Evaluation

Copying leads us into dealing with temporaries: do you first allocate all
temporaries in new matrices and then analyse lifetimes and dimensions to figure
out which slots of memory can be re-used? Or do you try and infer the available
resources from the environment as you go?  Can, and should, you type arrays and
matrices (or $n$-dimensional tensors) as the same?

Adding in more and more considerations, the problem starts to resemble register
allocation: there are registers of different types and sizes, many instructions
to choose from, a cost model to take into account all whilst trying to balance
the number of registers in use and the number of instructions emitted.

@@

So once you have written your memory-optimised program with all the features
and support provided by LT4LA and made it produce well-typed, compilable OCaml
code, the question then becomes, how to use this code. This process will vary
across ecosystems, but within OCaml, the new build-system on the block
\emph{Dune} has support for generating, compiling and linking OCaml modules at
\emph{compile time} (Figure~\ref{fig:build}). Indeed, this is how I have written
tests and benchmarks for programs produced by LT4LA from within OCaml. In
particular, I can use my linearly-typed Kalman filter implementation just like
and with any other OCaml function.

\begin{figure}[t]
    \centering
    \includegraphics[width=\textwidth]{impl_build}
    \caption{Using LT4LA functions from OCaml with the Dune
        build-system.}\label{fig:build}
\end{figure}

>>>>

Copying leads us into dealing with temporaries: do you first allocate all
temporaries in new matrices (SSA-style) and then analyse dimensions to figure
out which slots of memory can be re-used via copy coalescing? Or do you try and
infer the live ranges of available resources from the environment as you go?
Can, and should, you type arrays and matrices (or $n$-dimensional tensors) as
the same?

Adding in more and more considerations, the problem starts to resemble register
allocation: there are registers of different types and sizes, many
(non-orthogonal) instructions to choose from, a cost model to take into account
all whilst trying to balance the number of registers in use and the number of
instructions emitted.

@@

So once you have written your memory-optimised program with all the features
and support provided by LT4LA and made it produce well-typed, compilable OCaml
code, the question then becomes, how to use this code. This process will vary
across ecosystems, but within OCaml, the new build system on the block
\emph{Dune} has support for generating, compiling and linking OCaml modules at
\emph{compile time} (Figure~\ref{fig:build}). Indeed, this is how I have written
tests and benchmarks for programs produced by LT4LA from within OCaml. In
particular, I can use my linearly-typed Kalman filter implementation just like
and with any other OCaml function.

\begin{figure}[t]
    \centering
    \includegraphics[width=\textwidth]{impl_build}
    \caption{Using LT4LA functions from OCaml with the Dune
        build system.}\label{fig:build}
\end{figure}
